Automatic Syntactic MT Evaluation with Expected Dependency Pair Match\protect\blindthis{\Thanks{Thanks to Kevin Knight for providing data for earlier revisions of this research.}}

### 2009-05-08 edpm-paper.tex
monkeying with original edpm-paper to use mean-subtracted

  From these results, we design a new scoring metric ``Expected
  Dependency Pair Match'' (\myEDPM), and 
%   explore \myEDPM's quality
%   with respect to the GALE % \cite{olive06gale}
%   2.5 evaluations corpus.  We 
  demonstrate that $\Delta$\myEDPM{} is superior to $\Delta$BLEU and
  $\Delta$TER as a per-document and per-sentence predictor of
  $\Delta$HTER.
% , and is superior to $\Delta$TER in
%   the written contexts (newswire and web text).
\end{abstract}

@@

\subsection{Prediction of $\Delta$HTER per-document}

We evaluate our new measure \myEDPM{} by testing its prediction of
improvements in HTER over different translations of a document.
We name one of the three translation systems arbitrarily as baseline
$b$ and define
\begin{eqnarray}
  \label{eq:delta}
  \Delta s(i,b,z) & = & s(t_{i,z}) - s(t_{i,b})
\end{eqnarray}
as a measure of change % in measure $s$
that system $z$ provides over segment $i$ with respect to system $b$
(by providing translation $t_{i,z}$ instead of $t_{i,b}$).
% $\Delta_b(s,t_{i,z})$ may be either positive or negative.

We would like an automatic measure $s$ that provides a good
correlation $r$ between $\Delta s$ and $\Delta \textsc{hter}$.  For
each of the 516 documents\footnote{Using per-document comparison
  avoids the problems of per-sentence comparisons, e.g.\ that BLEU
  falls to zero too easily on a sentence.} in the corpus described in
table~\ref{tab:galestats}, for each of the three pairs of systems, we
generate the $\Delta s$ scores, ordering the systems such that
$\Delta\textsc{hter} \geq 0$ for each document pair.

>>>>

  From these results, we design a new scoring metric ``Expected
  Dependency Pair Match'' (\myEDPM), and 
  demonstrate that mean-subtracted \myEDPM{} is superior to
  mean-subtracted BLEU and
  mean-subtracted TER as a per-document and per-sentence predictor of
  mean-subtracted HTER.
\end{abstract}

@@

\subsection{Prediction of mean-subtracted HTER per-document}

We evaluate our new measure \myEDPM{} by testing its prediction of
improvements in HTER over different translations of a document.
Rather than consider absolute scores $s$ per-document, we normalize for
the underlying difficulty of the document by examining $\mu s(t)$, the difference
of translation $t_i$ from the mean score over the $I$ translations of
the same document, where 
\begin{equation}
  \label{eq:meansub}
  \mu s(t_i) = s(t_i) - \sum_{j=1}^I\frac{s(t_j)}{I}
\end{equation}

We would like an automatic measure $s$ that provides a good
correlation $r$ between $\mu s$ and $\mu \textsc{hter}$.  For
each of the 516 documents\footnote{Using per-document comparison
  avoids the problems of per-sentence comparisons, e.g.\ that BLEU
  falls to zero too easily on a sentence.} in the corpus described in
table~\ref{tab:galestats}, for each of the three pairs of systems, we
generate the $\mu s$ scores, calculating a mean for ea.
